All numerical experiments have been performed by a desktop class computer with the following relevant technical specifications:

\begin{itemize}[noitemsep]
  \item \textbf{Processor:} \textit{AMD Ryzen 9 3900X}. \\
    12 cores / 24 threads, \SI{3.8}{\giga\hertz} base clock / \SI{4.6}{\giga\hertz} boost clock.
  \item \textbf{Graphics card:} \textit{MSI GeForce 2070 Super}. \\
    \SI{8}{\giga\byte} GDDR6 VRAM, \SI{1605}{\mega\hertz} clock speed, \SI{9.062}{\tera\flops} @ 32-bit.
  \item \textbf{Memory:} \textit{Corsair Vengeance LPX DDR4 \SI{3200}{\mega\hertz} 32GB}.
  \item \textbf{Storage:} \textit{Intel 660p 1TB M.2 SSD}. \\
    Up to \SI{1800}{\mega\byte\per\second} read and write speed.
\end{itemize}

\begin{wrapfigure}[8]{r}{.4\textwidth}
  \vspace{-0.75\baselineskip}
  \fbox{\begin{minipage}{\dimexpr\linewidth-2\fboxrule-2\fboxsep}
    \begin{flushleft}
      \small
      \begin{center}\textbf{Model performance}\end{center}
      \begin{itemize}[nosep,leftmargin=*]
        \item \SI{218}{\milli\second} per training step (batch 16) \\
          $\implies$ \SI{14}{\milli\second} per sample.
        \item \SI{11}{\minute} per training epoch \\
          $\implies \approx \SI{18.3}{\hour}$ per experiment.
        \item \SI{8}{\milli\second} per prediction (batch 1) \\
          $\implies$ 125 predictions per \si{\second}.
      \end{itemize}
    \end{flushleft}
  \end{minipage}}
\end{wrapfigure}
\noindent
With a batch size of 16, each training step requires \SI{218}{\milli\second} of computation, resulting in approximately \SI{14}{\milli\second} per geographic tile.
When including the streaming of data from disk, updating weights based \num{2809} training batches of size 16, validating the model on \num{605} additional validation batches, and executing various Keras callbacks, each epoch lasts for 11 minutes from end to end.
Most experiments have been trained for 100 epochs, hence requiring altogether 18 hours and 20 minutes of training.
The final models are able to produce 125 predictions of size $\SI{256}{\pixel} \times \SI{256}{\pixel}$ per second.
